Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-05 Documents/Paper/ms.tex
Ewan

\section*{Acknowledgements}
This work is supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand. I would like to thank the following
people for valuable conversations and inspiration:
Anna Pancoast (UCSB), David Hogg (NYU), Daniel Foreman-Mackey (NYU),
Courtney Donovan (Auckland), Tom Loredo (Cornell), Iain Murray (Edinburgh),
John Skilling (MaxEnt Data Consultants), and Daniela Huppenkothen
(Amsterdam, NYU).

>>>>

\section*{Acknowledgements}
This work is supported by a Marsden Fast-Start grant
from the Royal Society of New Zealand. I would like to thank the following
people for valuable conversations and inspiration:
Anna Pancoast (UCSB), David Hogg (NYU), Daniel Foreman-Mackey (NYU),
Courtney Donovan (Auckland), Tom Loredo (Cornell), Iain Murray (Edinburgh),
Ewan Cameron (Oxford),
John Skilling (MaxEnt Data Consultants), and Daniela Huppenkothen
(Amsterdam, NYU).
